Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-06-08 Master Thesis/synopsis.tex
Finally fix proof of 3.2!

Let $w_1,w_2 \in\operatorname{Spv}_\text{d}^{(2)}(K)$ be two different valuations. By Lemma \ref{2.2}, the following statements are equivalent:
\begin{enumerate}[(i)]
\item The composite $K_{w_1}K_{w_2}$ is not algebraically closed.
\item $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ and $v(w_1) = v(w_2)$.
\end{enumerate}
If (ii) holds, $k(v)$ is separably closed where $v=v(w_1)$. By Lemma \ref{lemma-henselization-specialization} we have $K_{w_1}K_{w_2}\subset K_v^\text{t}$ and by Theorem \ref{theorem-absoluteinertia} (ii) $K_{w_1}K_{w_2}$ is the absolute inertia field $K_v^\text{t}$ of $K_v$. Furthermore, $K'_{w'_1}K'_{w'_2} = (K_{w_1}K_{w_2})' \neq \overline{K'}$ and again by Lemma \ref{2.2} we get: \[w'_1,w'_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)\quad \text{and} \quad v(w'_1) = v(w'_2)\]
Thus $\sigma: \operatorname{Spv}_\text{d}^{(2)}(K)\to \operatorname{Spv}_\text{d}^{(2)}(K')$ maps $\operatorname{Spv}_\text{rd}^{(2)}(K)$ onto $\operatorname{Spv}_\text{rd}^{(2)}(K')$ such that:
\[ v(w_1)=v(w_2) \iff v(w'_1) = v(w'_2) \]
Let $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$. Since $v\not\in |\operatorname{Spv}(K)|$, there exists a $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ such that $v(w)=v$. We define $v'=v(w')$. This shows that $\sigma$ also induces a bijection: 
\[\sigma:\operatorname{Spv}_\text{d}^{(1)}(K)\to\operatorname{Spv}_\text{d}^{(1)}(K'),\ v\mapsto v'\] 
This map is well-defined and for all $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ we have $\sigma(v(w)) = v(\sigma(w))$.

>>>>

Let $w_1,w_2 \in\operatorname{Spv}_\text{d}^{(2)}(K)$ be two different valuations. Then the following statements are equivalent:
\begin{enumerate}[(i)]
\item The composite $K_{w_1}K_{w_2}$ is not algebraically closed.
\item $w_1,w_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ and $v(w_1) = v(w_2)$.
\end{enumerate}
The implication (i)$\implies$(ii) follows from Lemma \ref{2.2}. Now assume (ii) holds. Then $k(v)$ is separably closed where $v=v(w_1)$. By Lemma \ref{lemma-henselization-specialization} we have $K_{w_1}K_{w_2}\subset K_v^\text{t}$ and by Theorem \ref{theorem-absoluteinertia} (ii) $K_{w_1}K_{w_2}=K_v^\text{t}$. The extension of $v$ on $K_v^\text{t}$ has value group $\Gamma_v$, which is finitely generated. However, value groups of valuations on an algebraically closed field are divisible, hence $K_v^\text{t}$ can't be algebraically closed.

Furthermore, in this case, $K'_{w'_1}K'_{w'_2} = (K_{w_1}K_{w_2})' \neq \overline{K'}$ and again by Lemma \ref{2.2} we get: \[w'_1,w'_2\in\operatorname{Spv}_\text{rd}^{(2)}(K)\quad \text{and} \quad v(w'_1) = v(w'_2)\]
Thus $\sigma: \operatorname{Spv}_\text{d}^{(2)}(K)\to \operatorname{Spv}_\text{d}^{(2)}(K')$ maps $\operatorname{Spv}_\text{rd}^{(2)}(K)$ onto $\operatorname{Spv}_\text{rd}^{(2)}(K')$ such that:
\[ v(w_1)=v(w_2) \iff v(w'_1) = v(w'_2) \]
Let $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$. Since $v\not\in |\operatorname{Spv}(K)|$, there exists a $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ such that $v(w)=v$. We define $v'=v(w')$. This shows that $\sigma$ also induces a bijection: 
\[\sigma:\operatorname{Spv}_\text{d}^{(1)}(K)\to\operatorname{Spv}_\text{d}^{(1)}(K'),\ v\mapsto v'\] 
This map is well-defined and for all $w\in\operatorname{Spv}_\text{rd}^{(2)}(K)$ we have $\sigma(v(w)) = v(\sigma(w))$.
